full title

### 2020-11-21 paper/pldi21/abstract.tex
Revising inreds.

In this paper, we propose a novel technique to take advantage of the
high performance of dynamic analysis for JavaScript static analysis
in a sound way by using \textit{dynamic shortcuts}.  A dynamic shortcut
consists of three parts: 1) converting an abstract state to its corresponding
\textit{sealed symbolic state}, 2) performing \textit{sealed symbolic execution}
on the sealed symbolic state, and 3) converting a sealed symbolic state
to its corresponding abstract state. By taking dynamic shortcuts
during static analysis, we can significantly improve the analysis
scalability and precision by using highly-optimized commercial JavaScript engines
and lessen the modeling efforts by performing sealed symbolic execution for opaque code.
We formally define static analysis using dynamic shortcuts in the abstract
interpretation framework.  We actualize the technique via $\tool$, an
extended combination of SAFE and Jalangi, a static analyzer and a
dynamic analyzer, respectively.  We evaluated $\tool$ using
\inred{77} official tests of Lodash 4 library.
Our experiment shows that $\tool$ is \inred{X.X}x faster than the
baseline static analyzer on average, and it improves \inred{XX.XX}\%
of the analysis precision on average by using sealed symbolic
execution for \inred{XX.X} opaque functions.
\end{abstract}

>>>>

In this paper, we propose a novel technique to take advantage of the
high performance of dynamic analysis for JavaScript static analysis
in a sound way by using \textit{dynamic shortcuts}.  A dynamic shortcut
consists of three parts: 1) converting an abstract state to its corresponding
\textit{sealed symbolic state}, 2) performing \textit{sealed symbolic execution}
on the sealed symbolic state, and 3) converting a sealed symbolic state
to its corresponding abstract state. By taking dynamic shortcuts
during static analysis, we can significantly improve the analysis
scalability and precision by using highly-optimized commercial JavaScript engines
and lessen the modeling efforts by performing sealed symbolic execution for opaque code.
We formally define static analysis using dynamic shortcuts in the abstract
interpretation framework.  We actualize the technique via $\tool$, an
extended combination of SAFE and Jalangi, a static analyzer and a
dynamic analyzer, respectively.  We evaluated $\tool$ using
269 official tests of Lodash 4 library.
Our experiment shows that $\tool$ is \inred{6.30}x faster than the
baseline static analyzer, and it improves the precision to
detect 6 more dead branches on average by using sealed symbolic execution for
\inred{12} opaque functions.
\end{abstract}

### 2020-11-21 paper/pldi21/conclusion.tex
Revising inreds.

\section{Conclusion}\label{sec:conclusion}
We presented a novel technique for JavaScript static analysis using \textit{dynamic shortcuts}.
It can significantly accelerate the JavaScript static
analysis by freely leveraging high performance of dynamic analysis for
concretely executable program parts.  To maximally use dynamic analysis during static analysis,
we proposed \textit{sealed symbolic execution}, which performs
concrete execution using sealed symbolic values for abstract values.
We formally defined static analysis using dynamic shortcuts in the
abstract interpretation framework and proved its soundness and termination.
We developed $\tool$ as a prototype implementation of the proposed approach
by extending a combination of the state-of-the-art static and dynamic
analyzers SAFE and Jalangi.  Our tool accelerates the speed
of static analysis \inred{X.X}x for original tests and \inred{X.X}x for
abstracted tests of Lodash 4 library.  Moreover, it improves \inred{XX.XX}\% of
the analysis precision by using sealed symbolic execution instead of
manual modeling for \inred{XX.X} opaque functions on average.

>>>>

\section{Conclusion}\label{sec:conclusion}
We presented a novel technique for JavaScript static analysis using \textit{dynamic shortcuts}.
It can significantly accelerate the JavaScript static
analysis by freely leveraging high performance of dynamic analysis for
concretely executable program parts.  To maximally use dynamic analysis during static analysis,
we proposed \textit{sealed symbolic execution}, which performs
concrete execution using sealed symbolic values for abstract values.
We formally defined static analysis using dynamic shortcuts in the
abstract interpretation framework and proved its soundness and termination.
We developed $\tool$ as a prototype implementation of the proposed approach
by extending a combination of the state-of-the-art static and dynamic
analyzers SAFE and Jalangi.  Our tool accelerates the speed
of static analysis \inred{19.96}x for original tests and \inred{6.30}x for
abstracted tests of Lodash 4 library.  Moreover, it detect \inred{6} more of
dead branches by using sealed symbolic execution instead of
manual modeling for \inred{12} opaque functions on average.

### 2020-11-21 paper/pldi21/intro.tex
Revising inreds.

The contributions of this paper include the following:
\begin{itemize}
\item We present a novel technique for JavaScript static
analysis to leverage the high performance of dynamic analysis using
dynamic shortcuts.  We formally define the technique and prove
its soundness and termination.
\item We actualize the proposed technique in $\tool$, an
extended combination of SAFE and Jalangi.
\item For empirical evaluation, we analyzed 269 official tests of
Lodash 4 library.  The experiment shows that $\tool$ outperforms
SAFE \inred{X.X}x on average.  Moreover, by using dynamic shortcuts
instead of manual modeling for \inred{XX.X} opaque functions,
$\tool$ improves the analysis precision to detect 6 more dead branches on
average.
\end{itemize}

>>>>

The contributions of this paper include the following:
\begin{itemize}
\item We present a novel technique for JavaScript static
analysis to leverage the high performance of dynamic analysis using
dynamic shortcuts.  We formally define the technique and prove
its soundness and termination.
\item We actualize the proposed technique in $\tool$, an
extended combination of SAFE and Jalangi.
\item For empirical evaluation, we analyzed 269 official tests of
Lodash 4 library.  The experiment shows that $\tool$ outperforms
SAFE \inred{6.30}x on average.  Moreover, by using dynamic shortcuts
instead of manual modeling for \inred{12} opaque functions,
$\tool$ improves the analysis precision to detect 6 more dead branches on
average.
\end{itemize}
